A Model for Extracting Time Delays from Noisy Time Series Data

### 2013-08-24 doc/Paper1/ms.tex
More covariance

Recall that the noise-free light curves of the two images are given by:
\begin{eqnarray}
y_1(t) &=& m_1 + q(t) + \mu_1(t) \\
y_2(t) &=& m_2 + q(t - \tau_2) + \mu_2(t) \\
\end{eqnarray}
Using this, and the model assumptions discussed above, we can obtain the
covariance of $y_1$ with itself at a different time, as well as $y_2$ with itself
at a different time and $y_1$ and $y_2$ at any time lag.

\begin{eqnarray}
\textnormal{Cov}\left[y_i(t_1), y_j(t_2)\right]
&=& \mathds{E}\left[\left(y_i(t_1) - m_i\right)\left(y_j(t_2) - m_j\right)\right]
\end{eqnarray}
where the intrinsic variations have been assumed to be uncorrelated with the
microlensing contributions.

>>>>

Recall that the noise-free light curves of the two images are given by:
\begin{eqnarray}
y_1(t) &=& m_1 + q(t - \tau_1) + \mu_1(t) \\
y_2(t) &=& m_2 + q(t - \tau_2) + \mu_2(t)
\end{eqnarray}
where $\tau_1 = 0$.
Using this, and the model assumptions discussed above, we can obtain the
covariance of $y_1$ with itself at a different time, as well as $y_2$ with itself
at a different time, and $y_1$ and $y_2$ at any time lag.

\begin{eqnarray}
\textnormal{Cov}\left[y_i(t_1), y_j(t_2)\right]\\
= \mathds{E}\left[\left(y_i(t_1) - m_i\right)\left(y_j(t_2) - m_j\right)\right]\\
= \mathds{E}\left[\left(q(t_1 - \tau_i) + \mu_i(t_1)\right)
\left(q(t_2 - \tau_j) + \mu_j(t_2)\right)\right]
\end{eqnarray}
